\section{Evidence} %% stories from Nabokov, analysis, what the ever
\label{evidence}

Taking this insight\textemdash that memory is both the location of the greatest experiences and readily accessible\textemdash as an axiom, we proceed to observe how Nabokov's characters leverage it.
We see that they consistently place great emphasis on memories, and that this bias obscures their view of the present. 
Thus old friends are judged by the memory they left behind regardless of whether they have or have not changed in the meantime.
This technique may lead to positive or negative results, but the real curiosity is how frequently it is used.

\vspace{1cm}
\subsection{Returning Characters}
To begin, we review a few of the ways in which protagonists from Nabokov's novels reappear in other works.
We see that characters reappear throughout his literary world as though it were a real community.
Interestingly, these old friends look almost exactly as they did when we last parted, raising suspicion about whether we are seeing them as they are or operating under some bias.
%% We wonder, then, whether our visitors are accurate reflections of how the character is faring today or rather resurgent memories, echoing a past where they enjoyed center stage.

The first example of returning characters comes in \emph{The Luhzin Defense}, Nabokov's third novel. 
Here we meet for a second time Mary and Alfyorov, the title character of Nabokov's first book and her husband.
Alfyorov is the same talkative fool and Mary is still the silent angel.
As Luhzin's wife remarks: ``there is something a little mean and a little pathetic about [Alfyorov]''~\cite[The Defense, 152]{defense}.
On the other hand, Mary is just stunning.
``What a darling, what eyes,'' Mrs. Luhzin waxes~\cite[The Defense, 152]{defense}.
Apparently, years together have not softened Alfyorov nor hardened Mary. 
Indeed, Mary seems to have the same heavenly aura as she did in Ganin's youth. 
Curious, but not altogether impossible.

Next, we have the return of the Dreyers in \emph{Laughter in the Dark}. 
At the end of \emph{King, Queen, Knave}, Mrs. Dreyer had passed away yet she returns to send an lunch invitation to Albinus and his wife just as Albinus's illicit relationship with Margot becomes public~\cite[86]{nabokov1960laughter}.
Perhaps they are alive and well, as the reader best remembers them rather than how they actually wound up.
Perhaps it is only the ghost of Mrs. Dreyer, trying to save Albinus's family from ruin.
Either way, the Dreyers make a return in a moment crucial to the happiness of another couple.

Numerous other characters make appearances in later novels, and here the examples number too many to count. 
Hermann appears, evil as sin, or sorry Humbert wanders on stage, let out for his yearly walk~\cite[xiii]{nabokov1989despair}.
Plus, later characters are mixes of previous ones, like Cincinnatus' wife Marfin'ka who is reminiscent of Mary.
Still, we never see a character change between appearances. 
Not once does a character return in a new setting, or with new prospects or values.
They forever remain as they were in their debut into Nabokov's literary world.
On one hand, one might argue that this is done so that the characters are recognizable.
There would be little point to a visit from, say, Pierre Delalande if he were drastically changed from his perfect, outrageous self.
Still, this practice denotes an inability to change and an inability to let go of the past. 
The lack of change is evident by the circumstances of each reappearance and the inability to let go is demonstrated by the fact that these characters appear at all in a book they play no obvious role in.

\vspace{1cm}
\subsection{Case Analysis}
Although thought-provoking, the fact that reappearing characters remain unchanged is not quite convincing that people in Nabokov's world remain static.
Thus, to further illustrate the point that characters use memory (oftentimes deliberately) as an alternative to the present, even to the point that the present is completely ignored or misunderstood, we examine cases and characters within the novels they appear.
In their respective books, these are the first-person characters\textemdash those to whom the rest of the world is relative. 
When we claimed within the introduction that the world never changes, only the first-person presence, we referred to these characters and their perception of their surroundings.

\vspace{1cm}
\input{harlequins}
\vspace{1cm}
\input{lolita}
\vspace{1cm}
\input{pnin}
\vspace{1cm}
\input{mary}

%% We also have characters reappeearing, and need a place to talk about that. Maybe after mary can go KingQueenKnave, which has a visit
%% or was it Laughter in the Dark?
