\section{Philosophy}
\label{philosophy}
%% NAME = _______
narcissistic, easy to 

\subsection{Relation to Stoicism}
The ancient philosophy of \emph{Stoicism} is one of the longest surviving ethical systems.
Originally developed in Athens during the $3^{\text{rd}}$ century BCE, stoicism heralded virture as the highest value~\cite{long1989hellenistic}.
A virtuous man would be rightfully happy, no matter the world around him.
\todo{more stoicism}

This is in contrast to other contemporary ethics, namely Aristotle's (expounded in his \emph{Nicomachean Ethics}~\cite{ross2009nicomachean}), which took a more scientific approach to happiness.
Virture was good, and a happy man was necessarily virtuous, but Aristotle noted that a person's happiness was very often contingent on the actions and opinions of their neighbors.
Rather than ignoring one's surroundings, a person should observe others in the community, mirroring their actions and following their beliefs.
In this way, he argued, one could find happiness even in a foreign land. 
Concsiousness and sensitivity to others would find accomodation in any environment.

%% TODO why did I mention Aristtotle?

\subsection{Relation to Narcissism}
Narcissism, defined by Freud as the investment of libidinal energy in the ego~\cite{frued}, is often recognized as overwhelming selfishness.
Narcissists are frequently classified as coarse, uncaring individuals who care nothing for those around them and focus exclusively on providing for their own needs.
Quick to take offense and unforgiving towards others, they are widely regarded as mentally unhealthy~\cite{narcissism-today}. 
However, narcissism is not altogether destructive.
Individuals with narcissistic traits are often found to have high self-esteem and interpersonal sensitivity~\cite{watson1992measures,watson1996self,rhodewalt1998narcissism,morf2001unraveling}.
Moreover, they are resilient against depression, social anxiety, and guilt~\cite{campbell2001narcissism}.
Far from being a wholly negative characteristic, the literature is split between the pro-self and anti-social dimensions of narcissism.
%% Explain more why narcissism is good?

\philo~offers similar benefits, in that happiness is more contingent on one's own actions than on others. \todo{explain this}

\philo~offers similar downsides.


\subsection{Relation to Binary Thinking}

